### 2018-03-17 paper/6-engineering.tex

We note that while all the simple implementations presented in
\S\ref{sec-implementations} can deal with non-determinism, some real build
systems, e.g. \Buck and \Bazel, rely on task determinism.

>>>>

Most of the implementations in \S\ref{sec-implementations} can deal with non-determinism,
apart from \Bazel and \Buck, which require deterministic execution, and in turn can
optimise the number of roundtrips required to the server.
